\Large The state learner -- a super learner for right-censored data

### 2025-01-13 manuscript/manuscript-wo-appendix.tex
biostats version

\documentclass[12pt]{article}
\usepackage[a4paper,left=2.8cm, right=2.8cm, top=3cm, bottom=3cm]{geometry}

@@

%% Line spacing
% \linespread{1.65}

@@

@@

We introduce our notation and framework in
Section~\ref{sec:framework}. In Section~\ref{sec:super-learning} we define
general super learning for right-censored data.
Section~\ref{sec:super-learner-simple} introduces the state learner, and
Section~\ref{sec:theor-results-prop} provides theoretical guarantees. In
Section~\ref{sec:targeted-learning} we discuss the use of the state learner in
the context of targeted learning. We report results of our numerical experiments
in Section~\ref{sec:numer-exper} and analyse a prostate cancer data set in
Section~\ref{sec:real-data-appl}. Section~\ref{sec:discussion} contains a
discussion of the merits and limitations of our proposal.
Appendices~\ref{sec:proof-proposition} and~\ref{sec:state-learner-with} contain
proofs. An implementation of the state learner is available at
\url{https://github.com/amnudn/statelearner} along with codes for reproducing
our numerical experiments.

@@

\begin{proposition}
  \label{prop:stric-prop}
  If \(P_0\in\mathcal{P}\) then
  \begin{equation*}
    F_0 = \argmin_{F \in \mathcal{H}_{\mathcal{P}}} P_0{[\bar{B}_\tau(F, \blank)]},
  % F^* = \argmin_{(\Lambda_1,\Lambda_2,\Gamma) \in \mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}} P_0{[\bar B_\tau(\phi_{(\Lambda_1,\Lambda_2,\Gamma)}, \blank)]},
  \end{equation*}
  \( H \)-almost surely for any \( j\in \{-1,0,1,2\} \) and almost any
  \( t \in [0, \tau]\).
\end{proposition}
\begin{proof}
  See Appendix~\ref{sec:proof-proposition}.
\end{proof}

@@

\begin{corollary}
  \label{cor:oracle-prop}
  For all \(P_0\in\mathcal{P}\), \( n \in \N \), \( k \in \{1, \dots, K\} \),
  and $\delta>0$,
  \begin{align*}
    \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    & \leq (1 + 2\delta)
      \E_{P_0}{\left[ \Vert \tilde{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    \\
    & \quad
      + (1+ \delta) 16   K \tau
      \left(
      13 + \frac{12}{\delta}
      \right)
      \frac{\log(1 + |\mathcal{F}_n|)}{n}.
  \end{align*}
\end{corollary}
\begin{proof}
  See Appendix~\ref{sec:proof-proposition}.
\end{proof}

@@

\begin{corollary}
  \label{cor:asymp-cons}
  Assume that \( |\mathcal{F}_n| = \bigO(n^q)\), for some \( q \in \N \) and
  that there exists a sequence \( \phi_n \in \mathcal{F}_n \), \( n \in \N \),
  such that
  \( \E_{P_0}{\left[ \Vert \phi_n(\data_n^{-k}) - F_{0} \Vert_{P_0}^2 \right]} =
  \bigO(n^{-\alpha}) \), for some \( \alpha\leq 1 \).
  \begin{enumerate}[label=(\alph*)]
  \item If $\alpha=1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2
      \right]} = \bigO(\log(n)n^{-1}) \).
  \item If $\alpha<1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]} =
    \bigO(n^{-\alpha}) \).
  \end{enumerate}
\end{corollary}
\begin{proof}
  See Appendix~\ref{sec:proof-proposition}.
\end{proof}

@@

    & P_0{\left[

@@

      \Gamma_0(s,\blank) -\hat{\Gamma}_n(s,\blank)

@@

      [\Lambda_0-\hat{\Lambda}_n]

@@

      P_0{\left[
      \int_0^{\tau} \int_0^{s} w^a_n(s,u,\blank) [F_0 - \hat{F}_n](u-, 0, \blank)[F_0 - \hat{F}_n](s-, 0, \blank) F_0(\diff u, 2, \blank ) F_0 ( \diff s, 1, \blank)

@@

      P_0{\left[
      \int_0^{\tau} \int_0^{s} w^b_n(s,u,\blank) [F_0 - \hat{F}_n](u-, 0, \blank)
      F_0(\diff u, 2, \blank ) [F_0 - \hat{F}_n](\diff s, 1, \blank)

@@

      P_0{\left[
      \int_0^{\tau} \int_0^{s} w^c_n(s,u,\blank) [F_0 - \hat{F}_n](\diff u, 2, \blank)
      [F_0 - \hat{F}_n](s-, 0, \blank)
      F_0(\diff s, 1, \blank ) 

@@

      P_0{\left[
      \int_0^{\tau} \int_0^{s} w^d_n(s,u,\blank) [F_0 - \hat{F}_n](\diff u, 2, \blank)
      [F_0 - \hat{F}_n](\diff s, 1, \blank)

@@

  See Appendix~\ref{sec:state-learner-with}.

@@

\appendix

\section{Theoretical guarantees for the state learner}
\label{sec:proof-proposition}

In this section we provide proofs of the results stated in
Section~\ref{sec:theor-results-prop}.

Define
\( \bar{B}_{\tau,0}(F, o) = \bar{B}_{\tau}(F, o) - \bar{B}_{\tau}(F_0, o) \) and
\( R_{0}(F) = P_0{[\bar{B}_{\tau,0}(F, \blank)]} \).
\begin{lemma}
  \label{lemma:norm}
  \( R_{0}(F) = \Vert F - F_0 \Vert_{P_0}^2 \), where \( \Vert \blank \Vert_{P_0}\) is defined
  in equation~(\ref{eq:norm}).
\end{lemma}
\begin{proof}[Proof]
  For any \( t \in [0, \tau] \) and \( j\in \{-1,0,1,2\} \) we have
  \begin{align*}
    & \E_{P_0}{\left[ (F(t, j, X) - \1{\{\eta(t) = j \}})^2 \right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X) + F_0(t, j, X) - \1{\{\eta(t) = j
      \}})^2 \right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))^2\right]}
      + \E_{P_0}{\left[ (F_0(t, j, X) - \1{\{\eta(t) = j \}})^2\right]}
    \\
    & \quad
      + 2\E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))(F_0(t, j, X) - \1{\{\eta(t) = j
      \}})\right]}
    \\
    & =    \E_{P_0}{\left[ (F(t, j, X) - F_0(t, j, X))^2\right]}
      + \E_{P_0}{\left[ (F_0(t, j, X) - \1{\{\eta(t) = j \}})^2\right]},
  \end{align*}
  where the last equality follows from the tower property. Hence, using Fubini,
  we have
  \begin{equation*}
    P{[\bar{B}_{\tau}(F, \blank)]}
    = \Vert F - F_0 \Vert_{P_0}^2 + P_0{[\bar{B}_{\tau}(F_0, \blank)]}.
  \end{equation*}
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:stric-prop}]
  The result follows from Lemma~\ref{lemma:norm}.
\end{proof}

Recall that $\mathcal{H}_{\mathcal{P}}$ denote the function space consisting of
all conditional state occupation probability functions for some measure
\( P \in \mathcal{P} \).

\begin{proof}[Proof of Corollary~\ref{cor:oracle-prop}]
  First note that minimising the loss \( \bar{B}_{\tau} \) is equivalent to
  minimising the loss \( \bar{B}_{\tau,0} \), so the discrete super learner and
  oracle according to \( \bar{B}_{\tau} \) and \( \bar{B}_{\tau,0} \) are
  identical. By Lemma~\ref{lemma:norm}, \( R_0(F) \geq 0 \) for any
  \( F \in \mathcal{H}_{\mathcal{P}} \), and so using Theorem 2.3 from \citep{vaart2006oracle} with
  \( p=1 \), we have that for all \( \delta >0 \),
\begin{align*}
  & \E_{P_0}{\left[ R_0(\hat{\phi}_n(\data_n^{-k})) \right]}
  \\
  &  \quad \leq
    (1+2\delta)\E_{P_0}{\left[ R_0(\tilde{\phi}_n(\data_n^{-k})) \right]}
  \\
  & \qquad + (1+\delta) \frac{16 K}{n}
    \log(1 + |\mathcal{F}_n|)\sup_{F \in \mathcal{H}_{\mathcal{P}}}
    \left\{
    M(F) + \frac{v(F)}{R_0(F)}
    \left(
    \frac{1}{\delta} + 1
    \right)
    \right\}
\end{align*}
where for each \( F \in \mathcal{H}_{\mathcal{P}} \), \( (M(F), v(F)) \) is some Bernstein pair for
the function \(o \mapsto \bar{B}_{\tau,0}(F, o) \). As
\( \bar{B}_{\tau,0}(F, \blank) \) is uniformly bounded by \( \tau \) for any
\( F \in \mathcal{H}_{\mathcal{P}} \), it follows from section 8.1 in \citep{vaart2006oracle} that
\( (\tau, 1.5 P_0{[\bar{B}_{\tau,0}(F, \blank)^2]}) \) is a Bernstein pair for
\( \bar{B}_{\tau,0}(F, \blank) \). Now, for any \( a,b,c \in \R \) we have
\begin{align*}
  (a-c)^2 - (b-c)^2
  & = (a-b+b-c)^2 - (b-c)^2
  \\
  & = (a-b)^2 + (b-c)^2 +2(b-c)(a-b) - (b-c)^2
  \\
  & = (a-b)
    \left\{
    (a-b) +  2(b-c)
    \right\}
  \\
  & = (a-b)
    \left\{
     a + b -2c
    \right\},
\end{align*}
so using this with \( a=F(t, j, x) \), \( b=F_0(t, j, x) \), and
\( c = \1{\{\eta(t) = j\}} \), we have by Jensen's inequality
\begin{align*}
  & P_0{[\bar{B}_{\tau,0}(F, \blank)^2]}
  \\
  & \leq
    2\tau\E_{P_0}{\left[
    \sum_{j=-1}^{2} \int_0^{\tau}
    \left\{
    \left(
    F(t, j, X) - \1{\{\eta(t) = j\}}
    \right)^2
    -
    \left(
    F_0(t, j, X) - \1{\{\eta(t) = j\}}
    \right)^2
    \right\}^2
    \diff t 
    \right]}
  \\
  & =2\tau
    \E_{P_0}\Bigg[
    \sum_{j=-1}^{2} \int_0^{\tau}
    \left(
    F(t, j, X) - F_0(t, j, X)
    \right)^2
  \\
  & \quad \quad \quad\quad \quad \quad \times
    \left\{
    F(t, j, X) +  F_0(t, j, X)-2 \1{\{\eta(t) = j\}}
    \right\}^2
    \diff t 
    \Bigg]
  \\
  & \leq
    8\tau \E_{P_0}{\left[
    \sum_{j=-1}^{2} \int_0^{\tau}
    \left(
    F(t, j, X) - F_0(t, j, X)
    \right)^2
    \diff t 
    \right]}.
  \\
  & =
    8\tau \Vert F - F_0 \Vert_{P_0}^2.
\end{align*}
Thus when \( v(F) = 1.5 P_0{[\bar{B}_{\tau,0}(F, \blank)^2]} \) we have by
Lemma~\ref{lemma:norm}
\begin{equation*}
  \frac{v(F)}{R_0(F)}
  = 1.5 \frac{P_0{[\bar{B}_{\tau,0}(F, \blank)^2]}}{P_0{[\bar{B}_{\tau,0}(F, \blank)]}}
  \leq 12 \tau,
\end{equation*}
and so using the Bernstein pairs \( (\tau, 1.5 P_0{[\bar{B}_{\tau,0}(F, \blank)^2]}) \) we have
\begin{equation*}
  \sup_{F \in \mathcal{H}_{\mathcal{P}}}
  \left\{
    M(F) + \frac{v(F)}{R_0(F)}
    \left(
      \frac{1}{\delta} + 1
    \right)
  \right\}
  \leq \tau
  \left(
    13 + \frac{12}{\delta}
  \right),
\end{equation*}
For all $\delta>0$ we thus have
\begin{align*}
  \E_{P_0}{\left[ R_0(\hat{\phi}_n(\data_n^{-k})) \right]}
  \leq
  &(1+2\delta)\E_{P_0}{\left[ R_0(\tilde{\phi}_n(\data_n^{-k})) \right]}
  \\
  & \quad
    + (1+\delta)\log(1 + |\mathcal{F}_n|) \tau \frac{16 K}{n}
    \left(
    13 + \frac{12}{\delta}
    \right),
\end{align*}
and then the final result follows from Lemma~\ref{lemma:norm}.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:asymp-cons}]
  By definition of the oracle and Lemma~\ref{lemma:norm},
  \begin{equation*}
    \E_{P_0}{\left[ \Vert \tilde{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2
      \right]} \leq \E_{P_0}{\left[ \Vert \phi_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2
      \right]}  
  \end{equation*}
  for all \( n \in \N \). The results then follows from
  Corollary~\ref{cor:oracle-prop}.
\end{proof}

\section{The state learner with targeted learning}
\label{sec:state-learner-with}

In this section show that a product structure is preserved when an estimator
$\bar\Psi(\hat{F}_n, \hat{H}_n)$ is used instead of
$\tilde\Psi(\hat{\Lambda}_n, \hat{\Gamma}_n, \hat{H}_n)$.

\begin{proof}[Proof of Proposition~\ref{prop:dr-structure}]
  For notational convenience we suppress \( X \) in the following. The final
  result can be obtained by adding the argument \( X \) to all functions and
  averaging. We use the relations from equation~(\ref{eq:7}) to write
  \begingroup %
  \allowdisplaybreaks
    \begin{align*}
      & \int_0^{\tau} w(s) 
        \left\{
        \Gamma(s) - \hat{\Gamma}_n(s)
        \right\}
        [\Lambda - \hat{\Lambda}_n](\diff s)
      \\
      & =
        \int_0^{\tau} w(s) 
        \left\{
        \int_0^s \frac{F(\diff u, 2)}{F(u-, 0)} -
        \int_0^s \frac{\hat{F}_n(\diff u, 2)}{\hat{F}_n(u-, 0)}  -
        \right\}
        \left[
        \frac{F(\diff s, 1)}{F(s-, 0)}
        - \frac{\hat{F}_n(\diff s, 1)}{\hat{F}_n(s-, 0)}
        \right]
      \\
      & =
        \int_0^{\tau} w(s) 
        \Bigg\{
        \int_0^s 
        \left(
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) F(\diff u, 2)
      \\
      & \qquad\qquad \qquad
        +
        \int_0^s \frac{1}{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, 2) - \hat{F}_n(\diff u, 2)
        \right]
        \Bigg\}
      \\
      & \qquad\qquad \times
        \left[
        \left(
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff s, 1)
        + \frac{1}{\hat{F}_n(s-, 0)}
        \left(
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right)
        \right]
      \\
      &
        = \int_0^{\tau} 
        \int_0^s
        w(s) 
        \left(
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) 
        \left(
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff u, 2)F(\diff s, 1)
      \\
      & \quad +
        \int_0^{\tau}
        \int_0^s
        w(s) 
        \left(
        \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
        \right) \frac{F(\diff u, 2) }{\hat{F}_n(u-,0)}
        \left(
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right)
      \\
      & \quad +
        \int_0^{\tau} 
        \int_0^s      
        \frac{w(s) }{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, 2) - \hat{F}_n(\diff u, 2)
        \right]
        \left(
        \frac{1}{F(s-, 0)} -
        \frac{1}{\hat{F}_n(s-, 0)}
        \right)F(\diff s, 1)
      \\
      & \quad +
        \int_0^{\tau} 
        \int_0^s      
        \frac{w(s) }{\hat{F}_n(u-, 0)} 
        \left[
        F(\diff u, 2) - \hat{F}_n(\diff u, 2)
        \right]
        \frac{1}{\hat{F}_n(s-, 0)}
        \left(
        F(\diff s, 1) -
        \hat{F}_n(\diff s, 1)
        \right).
    \end{align*}
    \endgroup %
    Consider the first term on the right hand side. Defining
  \begin{equation*}
    w_n^*(t)  = 
    \left(
      F(t-, 0)
      - \hat{F}_n(t-, 0)
    \right)
    \left(
      \frac{1}{F(t-, 0)}
      - \frac{1}{\hat{F}_n(t-, 0)}
    \right),
  \end{equation*}
  we can write
  \begin{align*}
    & \int_0^{\tau} 
      \int_0^s
      w(s) 
      \left(
      \frac{1}{F(u-, 0)} -  \frac{1}{\hat{F}_n(u-, 0)}
      \right)      
      \left(
      \frac{1}{F(s-, 0)} -
      \frac{1}{\hat{F}_n(s-, 0)}
      \right)F(\diff u, 2)F(\diff s, 1)
    \\
    & =
      \int_0^{\tau} 
      \int_0^s
      w(s)
      w_n^*(u) 
      \left(
      F(u-, 0) - \hat{F}_n(u-, 0)
      \right)
    \\
    & \qquad \qquad \quad
      \times
      w_n^*(s) 
      \left(
      F(s-, 0) - \hat{F}_n(s-, 0)
      \right)       
      F(\diff u, 2)F(\diff s, 1)
    \\
    & =
      \int_0^{\tau} 
      \int_0^s
      w_n^a(s,u)
      \left(
      F(u-, 0) - \hat{F}_n(u-, 0)
      \right)
      \left(
      F(s-, 0) - \hat{F}_n(s-, 0)
      \right)       
      F(\diff u, 2)F(\diff s, 1),
  \end{align*}
  where we have defined \( w_n^a(s,u) = w(s)w^*_n(s)w^*_n(u) \). By assumption,
  \( w_n^a(s,u) \) is uniformly bounded. The same approach can be applied to the
  three remaining terms which gives the result.
\end{proof}

>>>>

\documentclass[11pt]{article}
\usepackage[a4paper,left=2.8cm, right=2.8cm, top=3cm, bottom=3cm]{geometry}

@@

%% Line spacing
\linespread{2}

@@

\usepackage{endfloat}

@@

We introduce our notation and framework in Section~\ref{sec:framework}. In
Section~\ref{sec:super-learning} we define general super learning for
right-censored data. Section~\ref{sec:super-learner-simple} introduces the state
learner, and Section~\ref{sec:theor-results-prop} provides theoretical
guarantees. In Section~\ref{sec:targeted-learning} we discuss the use of the
state learner in the context of targeted learning. We report results of our
numerical experiments in Section~\ref{sec:numer-exper} and analyse a prostate
cancer data set in Section~\ref{sec:real-data-appl}.
Section~\ref{sec:discussion} contains a discussion of the merits and limitations
of our proposal. Proof are given in the supplementary material. An
implementation of the state learner is available at
\url{https://github.com/amnudn/statelearner} along with codes for reproducing
our numerical experiments.

@@

\begin{proposition}
  \label{prop:stric-prop}
  If \(P_0\in\mathcal{P}\) then
  \begin{equation*}
    F_0 = \argmin_{F \in \mathcal{H}_{\mathcal{P}}} P_0{[\bar{B}_\tau(F, \blank)]},
  % F^* = \argmin_{(\Lambda_1,\Lambda_2,\Gamma) \in \mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}\otimes\mathcal{M}_{\tau}} P_0{[\bar B_\tau(\phi_{(\Lambda_1,\Lambda_2,\Gamma)}, \blank)]},
  \end{equation*}
  \( H \)-almost surely for any \( j\in \{-1,0,1,2\} \) and almost any
  \( t \in [0, \tau]\).
\end{proposition}
\begin{proof}
  See Section~S1 of the Supplementary material.
\end{proof}

@@

\begin{corollary}
  \label{cor:oracle-prop}
  For all \(P_0\in\mathcal{P}\), \( n \in \N \), \( k \in \{1, \dots, K\} \),
  and $\delta>0$,
  \begin{align*}
    \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    & \leq (1 + 2\delta)
      \E_{P_0}{\left[ \Vert \tilde{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]}
    \\
    & \quad
      + (1+ \delta) 16   K \tau
      \left(
      13 + \frac{12}{\delta}
      \right)
      \frac{\log(1 + |\mathcal{F}_n|)}{n}.
  \end{align*}
\end{corollary}
\begin{proof}
  See Section~S2 of the Supplementary material.
\end{proof}

@@

\begin{corollary}
  \label{cor:asymp-cons}
  Assume that \( |\mathcal{F}_n| = \bigO(n^q)\), for some \( q \in \N \) and
  that there exists a sequence \( \phi_n \in \mathcal{F}_n \), \( n \in \N \),
  such that
  \( \E_{P_0}{\left[ \Vert \phi_n(\data_n^{-k}) - F_{0} \Vert_{P_0}^2 \right]} =
  \bigO(n^{-\alpha}) \), for some \( \alpha\leq 1 \).
  \begin{enumerate}[label=(\alph*)]
  \item If $\alpha=1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2
      \right]} = \bigO(\log(n)n^{-1}) \).
  \item If $\alpha<1$ then
    \( \E_{P_0}{\left[ \Vert \hat{\phi}_n(\data_n^{-k}) - F_0 \Vert_{P_0}^2 \right]} =
    \bigO(n^{-\alpha}) \).
  \end{enumerate}
\end{corollary}
\begin{proof}
  See Section~S2 of the Supplementary material.
\end{proof}

@@

    & P{\left[

@@

      \Gamma(s,\blank) -\hat{\Gamma}_n(s,\blank)

@@

      [\Lambda_1-\hat{\Lambda}_{1,n}]

@@

      \int_0^{\tau} \int_0^{s} w^a_n(s,u,\blank) [F - \hat{F}_n](u-, 0, \blank)[F - \hat{F}_n](s-, 0, \blank) F(\diff u, -1, \blank ) F ( \diff s, 1, \blank)

@@

      \int_0^{\tau} \int_0^{s} w^b_n(s,u,\blank) [F - \hat{F}_n](u-, 0, \blank)
      F(\diff u, -1, \blank ) [F - \hat{F}_n](\diff s, 1, \blank)

@@

      \int_0^{\tau} \int_0^{s} w^c_n(s,u,\blank) [F - \hat{F}_n](\diff u, -1, \blank)
      [F - \hat{F}_n](s-, 0, \blank)
      F(\diff s, 1, \blank ) 

@@

      \int_0^{\tau} \int_0^{s} w^d_n(s,u,\blank) [F - \hat{F}_n](\diff u, -1, \blank)
      [F - \hat{F}_n](\diff s, 1, \blank)

@@

  See Section~S3 of the Supplementary material.

@@

\section{Competing interests}
No competing interest is declared.
